Robust Co-occurrence Quantification for Lexical Distributional Semantics

### 2016-06-10 figures/interaction-cds.tex

\begin{figure*}
  \centering
    \centerline{\includegraphics[width=1.11\textwidth]{supplement/figures/SimLex999-interaction-cds}}
    \caption{\textbf{The effect of context probability estimation and smoothing on SimLex-999.}}
    \label{fig:interaction-cds}
\end{figure*}

>>>>

\begin{figure*}
  \centering
    \centerline{\includegraphics[width=1.11\textwidth]{supplement/figures/SimLex999-interaction-cds}}
    \caption{{\bf Effect of PMI variant (\texttt{discr}), smoothing (\texttt{cds}) and frequency weighting (\texttt{freq}) on SimLex-999.} Error bars correspond to a 95\% confidence interval as the value is estimated by averaging over all the values of the omitted parameters: \texttt{neg} and similarity.}
    \label{fig:interaction-cds}
\end{figure*}

### 2016-06-10 figures/interaction-neg.tex

\begin{figure*}
  \centering
    \centerline{\includegraphics[width=1.11\textwidth]{supplement/figures/SimLex999-interaction-neg}}
    \caption{\textbf{The behaviour of shifted PMI (SPMI) on SimLex-999.} \texttt{discr=spmi}, \texttt{freq=1} and \texttt{neg=1} corresponds to positive PMI.}
    \label{fig:interaction-neg}
\end{figure*}

>>>>

\begin{figure*}
  \centering
    \centerline{\includegraphics[width=1.11\textwidth]{supplement/figures/SimLex999-interaction-neg}}
    \caption{\textbf{The behaviour of shifted PMI (SPMI) on SimLex-999.} \texttt{discr=spmi}, \texttt{freq=1} and \texttt{neg=1} corresponds to positive PMI. Error bars correspond to a 95\% confidence interval as the value is estimated by averaging over all the values of the omitted parameters: \texttt{cds} and similarity.}
    \label{fig:interaction-neg}
\end{figure*}
